\documentclass[11pt,a4paper]{moderncv}

% moderncv theme
\moderncvtheme[grey]{classic}

% character encoding
\usepackage[utf8]{inputenc}

% page margin
\usepackage[scale=0.8]{geometry}
\usepackage{textcomp}

% personal data
\firstname{Jishnu Mohan}
\familyname{}
\address{Navaneetham, Pollethai P.O,}{688567, Alappuzha, Kerala, India}
\mobile{+91 9895 86 85 18}
\phone{+91 4782 86 41 71}
\email{jishnu7@gmail.com}
\homepage{j15h.nu}
%\photo[64pt]{picture}
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\begin{document}
\maketitle


\section {Personal Information}
    \cvline{Date of Birth}{14 Nov, 1989}
    \cvline{Sex}{Male}
    %\cvline{Work Experience}{3{\textonehalf} years as Software Engineer.}

\section{Education}
    \cventry{2007 -- 2011}{Bachelors degree in Information Technology}{MES College of Engineering}{}{}{University of Calicut, Kerala, India}

\section{Technical skills}
    \cvcomputer{Languages / APIs / Tools}
           {Javascript, Python, PHP, MySQL, HTML/HTML5, CSS/CSS3, Shell Scripting, Node, Less}
           {\textbf{Version Control}: }
           {Git, Subversion, bzr}

    \cvcomputer{Authoring \& Graphics }
           {{\LaTeX}, {\LaTeX} Beamer, LibreOffice/OpenOffice, Gimp, Inkscape, Blender, Adobe Photoshop, Adobe Flash}
           {\textbf{CMS \& Frameworks}: }
           {Drupal, Wordpress, Flask, Codeigniter, Backbone.js, Undersscore.js, GameClosure, Memacached, mocha.js, jsio, express.js}

    \cvcomputer{Languages / APIs / Tools - Familiar: }
           {C, C++, Android App development, Lua}{}{}

    \cvline{Platforms}{GNU/Linux (Arch linux, Debian, Ubuntu \& Fedora)}

%\pagebreak

\section{Work Experience}
    \cventry{2012 Nov -- Till date}{Hashcube Technologies}{Software Engineer}{\small{\url{http://hashcube.com}}}{}{
      %\cvline{}{}
      %\cvline{Project}{\textbf{Bubble Quest (Working title)}}
      %\cvline{}{Bubble Quest is a casual puzzle game. \newline Working as engineering lead and handling 9 resources.}
      %\cvline{Duration}{2014 August - till date}
      %\cvline{Technologies}{Javascript, GameClosure, Node}
      %\cvline{}{}
      %\cvline{Project}{\textbf{Sudoku Quest Mobile}}
      %\cvline{}{Worked as software developer in rewriting Sudoku Quest for iOS and Android. \newline \url{http://sudokuquest.com/}}
      %\cvline{Duration}{2013 March - till date}
      %\cvline{Technologies}{Javascript, GameClosure, Java, PHP}
      %\cvline{}{}
      %\cvline{Project}{\textbf{Sudoku Quest}}
      %\cvline{}{Sudoku Quest is the most popular sudoku game on facebook.\newline Worked as software developer, managing front-end as well as the back-end. \newline \url{https://apps.facebook.com/sudokuquest/}}
      %\cvline{Duration}{2012 November - till date}
      %\cvline{Technologies}{PHP, Javascript, HTML, CSS, Less}
      %\cvline{}{}
      %\cvline{Project}{\textbf{Dot Game}}
      %\cvline{}{Redesgined the UI and worked as software developer, managing \newline front-end as well as the backend. \newline \url{https://apps.facebook.com/connectdots/}}
      %\cvline{Duration}{2012 November - till date}
      %\cvline{Technologies}{PHP, Javascript, HTML, CSS, Less}
    }
    \cventry{2012 April -- 2012 Oct}{Accel Frontline (Ushus Tech division)}{Software Engineer Trainee}{}{\newline\small{\url{http://ushustech.com}}}{
      %\cvline{}{}
      %\cvline{Project}{\textbf{DLNA Media Player}}
      %\cvline{}{Goal of the project was to build an android media player with \newline the support for DLNA streaming. Worked as software developer in this project.}
      %\cvline{Duration}{2012 June - 2012 October}
      %\cvline{Technologies}{Java}
      %\cvline{}{}
      %\cvline{Project}{\textbf{Pulse Audio}}
      %\cvline{}{Worked as software developer to cross compile pulse audio for \newline an embedded device.}
      %\cvline{Duration}{2012 April - 2012 June}
      %\cvline{Technologies}{C, Bash script}
    }
    \cventry{2011 Aug -- 2012 Feb}{Ubiqurio}{Software Engineer}{\small{\url{http://ubiqurio.com}}}{}{
      %\cvline{}{}
       %\cvline{Project}{\textbf{IndiaVibes.tv}}
       %\cvline{}{Worked as web developer in building a portal for puzzle based \newline online contest conducted by IndiaVibes.tv.}
       %\cvline{Duration}{2011 Aug - 2011 Sep}
       %\cvline{Technologies}{PHP, Javascript, HTML, CSS}
       %\cvline{}{}
       %\cvline{Project}{\textbf{Logobake.com}}
       %\cvline{}{Worked as web developer in building web portal to create vector logos.}
       %\cvline{Duration}{2011 Aug - 2012 Feb}
       %\cvline{Technologies}{PHP, Javascript, HTML, CSS}
    }

\pagebreak

\section{Personal Projects}
    \cvline{Title}{\textbf{Indic Keyboard}}
    \cvline{}{\small Indian language input method for Android devices. Started as free time project,
      later ICFOSS (International Centre for Free and Open Source Software, Govt. of Kerala) supported the project for intial release.
      Currently this has more than 160,000 downloads.
    }
    \cvline{Language}{Java, XML}
    \cvline{Year}{2013 Jan - till date}
    \cvline{Website}{\small{\url{https://play.google.com/store/apps/details?id=org.smc.inputmethod.indic}}}
    \cvline{Source}{\small{\url{https://github.com/smc/Indic-Keyboard}}}

    \cvline{Title}{\textbf{SMS Attendance}}
    \cvline{}{\small Daily attendance SMS alert for MES College of Engineering students. During the period when project was active, it had more than 2300 registered users (out of 2700 students).}
    \cvline{Language}{Python, PHP, MySQL}
    \cvline{Year}{2010 August - 2011 April}
    \cvline{Website}{\small{\url{http://attendance.thecodecracker.com/}}}
    \cvline{Source}{\small{\url{http://github.com/jishnu7/SMSAttendance}}}

    \cvline{Title}{\textbf{Unicalbot}}
    \cvline{}{\small Twitterbot to tweet updates from University of Calicut website. The bot checks for notifications, exam results and tweets about it.}
    \cvline{Language}{Python, Twitter API}
    \cvline{Year}{2011 May - 2011 December}
    \cvline{Website}{\small{\url{http://unical.thecodecracker.com/}}}
    \cvline{Source}{\small{\url{http://github.com/jishnu7/Unical-Notifier}}}

    \cvline{Title}{\textbf{Yet Another 2048}}
    \cvline{}{\small Popular web based puzzle game 2048, re-written and optimized for mobile.}
    \cvline{Language}{Javascript}
    \cvline{Year}{2014 Feb - 2014 April}
    \cvline{Website}{\small{\url{https://play.google.com/store/apps/details?id=in.androidtweak.twozerofoureight}}}
    \cvline{Source}{\small{\url{https://github.com/jishnu7/Yet-Another-2048}}}

%\pagebreak

    \cvline{Title}{\textbf{DeskWiki Editor}}
    \cvline{}{\small A desktop client to edit MediaWiki websites. MediaWiki is a free and open source wiki software. Goal of this project was to provide offline editting.}
    \cvline{Year}{2011 Jan - 2011 April}
    \cvline{Language}{Python, GTK, MediaWiki API}
    \cvline{Source code}{\small{\url{https://code.launchpad.net/deskwiki}}}

    \cvline{Title}{\textbf{Blender Add-Ons}}
    \cvline{}{\small Developed a set of blender add-ons for architects. Blender is a free open source 3D content creation suite. Integrated library }
    \cvline{Language}{Python, Blender API}
    \cvline{Year}{2010 Oct - 2010 December}
    \cvline{Source code}{\small{\url{https://github.com/jishnu7/Solid-Wall, https://github.com/jishnu7/Integrated-Library}}}

    \cvline{Title}{\textbf{Publish Your Bookmarks}}
    \cvline{}{\small Simple tool to publish Firefox bookmarks as a webpage.}
    \cvline{Language}{PHP, Javascript, CSS}
    \cvline{Year}{2012 November - 2012 December}
    \cvline{Source code}{\small{\url{https://github.com/jishnu7/publish-your-bookmarks}}}


\section{Free/Libre/OpenSource Software Contributions}
    \cvline{Title}{\textbf{Silpa}}
    \cvline{}{Silpa is a web based language processing framework for Indian languages. Contributed to multiple modules and to the silpa server.}
    \cvline{Language}{Python, Javascript}
    \cvline{Website}{\small{\url{http://silpa.org.in}}}

    \cvline{Title}{\textbf{Game Closure}}
    \cvline{}{Javascript based cross platform game engine. Fixed multiple bugs and reported several issues.}
    \cvline{Language}{Javascript}
    \cvline{Website}{\small{\url{https://github.com/gameclosure}}}

    \cvline{Title}{\textbf{CyanogenMod}}
    \cvline{}{CyanogenMod is an android based open source replacement firmware for smart phones and tablets. Contributed to the input method of the project.}
    \cvline{Language}{Java / XML}
    \cvline{Website}{\small{\url{http://www.cyanogenmod.org/}}}

%\pagebreak

    \cvline{Title}{\textbf{jquery.i18n}}
    \cvline{}{jQuery based internationalization library. Fixed bugs in this project.}
    \cvline{Language}{Javascript}
    \cvline{Website}{\small{\url{https://github.com/wikimedia/jquery.i18n}}}

    \cvline{Title}{\textbf{jquery.ime}}
    \cvline{}{jQuery based input method editor library. Fixed several bugs in this project.}
    \cvline{Language}{Javascript}
    \cvline{Website}{\small{\url{https://github.com/wikimedia/jquery.ime}}}

    \cvline{}{Others}
    \cvline{GNOME Localization}{\small{\url{http://l10n.gnome.org}}}
    \cvline{SMC Fonts}{\small{\url{https://github.com/smc/fonts}}}
    \cvline{Devkit Helper}{\small{\url{https://github.com/hashcube/DevkitHelper}}}
    \cvline{Debian diaspora progressbar}{\small{\url{https://gitorious.org/debian-diaspora/progressbar}}}
    \cvline{Askbot}{\small{\url{http://askbot.org}}}


\section{Activities \& Achievements}
    \cvline{*}{\textbf{Google Summer of Code} (GSOC) Mentor - 2013 and 2014. \newline
      Attended GSOC Mentors summit, San Jose, California October 2014.}
    \cvline{*}{\textbf{SMS Attendance} and \textbf{Indic Keyboard} featured on national dailies, Deccan Chronicle, The Hindu, Times of India, Indian Express, Malayala Manorama and Mathrubhumi.}
    \cvline{*}{\textbf{Indic Keyboard} ranked \#1 in India, Saudi Arabia and UAE on top new free tools list.}
    \cvline{*}{DeskWiki was one of the 100+ selected applications in the \textbf{Ubuntu App Showdown} contest.}

\section{Blogs \& Social Media}
    \cvline{Github}{\url{http://github.com/jishnu7}}
    \cvline{Behance}{\url{https://www.behance.net/jishnu7}}
    \cvline{Personal/tech}{\url{http://blog.thecodecracker.com}}
    \cvline{Android blog}{\url{http://androidtweak.in}}


\end{document}
