% Template taken from : Aras Gungore (https://github.com/arasgungore/arasgungore-CV)
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small#2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\link}[2]{
  \emph{\href{#1}{\color{blue}#2}}
}

\newcommand{\projectlink}[2]{
  \href{#1}{#2}
}

\newcommand{\updateinfo}[1][\today]{\par\vfill\hfill{\scriptsize\color{gray}Last updated on #1}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \sffamily\mdseries\upshape Jishnu Mohan} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:9895868518}{+91 9895 868 518}
    $|$
    \faAt \hspace{.5pt} \href{mailto:resume@jishnu.xyz}{resume@jishnu.xyz}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/jishnu7}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/jishnu7}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://j15h.nu}{Portfolio}
\end{center}



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Languages / APIs / Tools:}{ Javascript, Python, PHP, MySQL, HTML/HTML5, CSS/CSS3, SCSS, Shell Scripting, Node, Less, MongoDB} \\ \vspace{3pt}
        \textbf{Languages / APIs / Tools - Familiar:}{ C, C++, Android app development, Lua, Objective C, iOS app development, Java, Debian packaging, Arch Linux packaging} \\ \vspace{3pt}
        \textbf{Frameworks / Libraries:}{ Flask, React, React-Native, Redux, Webpack, Vue.js, Backbone.js, GameClosure, Memcached, Mocha.js, jsio, Express.js, AngularJS, Babel, Amazon Alexa, Drupal, Wordpress, Ghost, Codeigniter} \\ \vspace{3pt}
        \textbf{Platforms}{ GNU/Linux (Arch Linux, Debian \& Ubuntu), AWS, Heroku, OpenShift, Google Cloud, Android, iOS} \\ \vspace{3pt}
        \textbf{Version Control:}{ Git, Subversion, bzr}
    }}
  \resumeSubHeadingListEnd



%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Forma (Formerly known as Twic)}{Fremont, CA - Remote from India}
      {Staff Software Engineer}{2019 April \textbf{--} 2024 Feb}
        \resumeItemListStart
           \resumeItem{Fintech product on Employee benefits space.}
           \resumeItem{Key part in defining code standards, crafting code guidelines, and supplying developers with tools to enforce them.}
           \resumeItem{I picked up features from the product management team, engaged in the development of architecture documents, test strategies, backend code work, frontend code, and supervised the entire process until deployment and testing were completed.}
           \resumeItem{Have been responsible for working on all aspects of the code base, spanning across the entire company.}
           \resumeItem{React based frontend work on employee portal and several internal frontend and backend projects.}
           \resumeItem{Worked on Google Cloud App engine, Cloud Functions, Firebase, AWS ElasticBeanstalk.}
           \resumeItem{Implemented SAML IdP and configure SSO with third party service providers.}
           \resumeItem{Worked on backend infrastructure and possibility of having VPC and VPN interconnecting Google Cloud, AWS and Mongo Atlas.}
           \resumeItem{Intiated and rewrote Angluar based mobile app in ReactNative.}
           \resumeItem{SCIM implementation to support Microsoft azure active directiores.}
           \resumeItem{Twilio based SMS handling.}
           \resumeItem{Built physical and virtual debit card issuance and transaction handling with Stripe.}
           \resumeItem{Key role in architecting new features.}
           \resumeItem{Providing guidance to developer team.}
        \resumeItemListEnd

    \resumeSubheading
      {Tarobites}{San Francisco, CA - Remote from India}
      {Software Engineer}{2016 Dec \textbf{--} 2019 Mar}
        \resumeItemListStart
          \resumeItem{Food tech product based in the bay area, California.}
          \resumeItem{Worked on tarobites.com customer facing website, backend APIs, chef web interface, admin web interface and mobile apps.}
          \resumeItem{Started with initial versions of the frontend with Angular.JS}
          \resumeItem{Lead role in rewriting the consumer facing frontend with React.JS.}
          \resumeItem{I helped with important internal projects, including the backend, operations help, and frontend code.}
          \resumeItem{Tackled all aspects of the code base, spanning the entire organization.}
          \resumeItem{Mentoring junior developers}
        \resumeItemListEnd

    \resumeSubheading{Hashcube Technologies}{Bangalore, India}{Senior Software Engineer \& Team Lead}{2012 Nov - 2016-Dec}
      \resumeItemListStart
        \resumeItem{Built \#1 Sudoku game - Sudoku Quest on Facebook platform with PHP based backend, Backbone.JS based frontend}
        \resumeItem{Handled deployment of games on company's own managed server on AWS.}
        \resumeItem{Worked on Dotgame, another popular game from the company - handled UI rewrite and player rankings.}
        \resumeItem{Key contribution in building mobile versions of the games with GameClosure 2D engine.}
        \resumeItem{Managed release processes on both Android and iOS app stores.}
        \resumeItem{Contributed bugfixes and features back to the open source GameClosure game engine.}
        \resumeItem{Created native modules for iOS and Android with Objective-C and Java with native APIs.}
        \resumeItem{Improved performance of the games on low RAM devices with code written on C/C++ and Javascript code optimization.}
        \resumeItem{Lead engineering team and key decision making role for the new game Gummy Pop.}
        \resumeItem{Supervised an engineering team of eight people.}
        \resumeItem{Worked on Alexa skill with python based backend and AWS ElasticBeanstalk.}
      \resumeItemListEnd

    \resumeSubheading{Accel Frontline - Ushus Tech}{Kochi, Kerala}{Software Engineering Trainee}{2012 April - 2012 Oct}
      \resumeItemListStart
      \resumeItem{DLNA Media Player: built an android media player with the support for DLNA streaming.}
      \resumeItem{Cross compile Linux Pulse Audio for a proprietary embedded device.}
      \resumeItemListEnd
    \resumeSubheading{Ubiqurio}{Kochi, Kerala}{Software Engineer}{2011 Aug - 2012 Feb}
      \resumeItemListStart
      \resumeItem{Worked on multiple website frontend and backend projects in PHP and Javascript}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------- AWARDS & ACHIEVEMENTS -----------


\vspace{5pt}
\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{2018 MOSS (Mozilla Open Source Support) Award:} {The organization responsible for the renowned browser Firefox presented me with an award for my contribution to the development of Indic Keyboard.}
        \\ \vspace{3pt}
        \textbf{Google Summer of Code:} {been a mentor for the years 2013, 2014 and 2016. }
        \\ \vspace{3pt}
        \textbf{SMS Attendance and Indic Keyboard featured in national media:} {Projects got featured on national dailies and online medias - Deccan Chronicle, The Hindu, Times of India, Indian Express, The Economic Times, Malayala Manorama, Deshabhimani, Mathrubhumi and Medianama.}
        \\ \vspace{3pt}
        \textbf{Indic Keyboard ranked \#1 on Google Play Store:} {On launch, the app was ranked \#1 in India, Saudi Arabia and UAE on top new free tools list.}
        \\ \vspace{3pt}
        \textbf{Ubuntu App Showdown:} {DeskWiki project was one of the 50 selected applications in the Ubuntu App Showdown contest.}
        \\ \vspace{3pt}
        \textbf{Yourstory.com article:} {Yourstory published a profile of me in their Techie Tuesdays column. -\link{https://yourstory.com/2017/03/techie-tuesdays-jishnu-mohan/}{Link}}
        \\ \vspace{3pt}
    }}
  \resumeSubHeadingListEnd



%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Indic Keyboard} $|$ \link{https://indic.app}{Website} \link{https://j15h.nu/source/keyboard}{Source}}{}
        \item{\small Mozilla Open Source Support Award (MOSS) winning Indian language input method for Android devices with more than \textbf{3 Million} downloads.
      }
      \resumeProjectHeading
        {\textbf{Yet Another 2048} $|$\link{https://j15h.nu/2048}{Web} \link{https://j15h.nu/source/2048}{Source}}{}
        \item{\small Popular web based puzzle game 2048, re-written and optimized for mobile.}

      \resumeProjectHeading
        {\textbf{DeskWiki Editor} $|$ \link{https://j15h.nu/source/wiki}{Source}}{}
        \item{\small A desktop client to edit MediaWiki websites.}

      %\resumeProjectHeading
        %{\textbf{AppRank.in} $|$ \link{https://apprank.in}{Website}}{}
        %\item{\small A website which tracks Google Play app rankings.}

      \resumeProjectHeading
        {\textbf{SMS Attendance} $|$ \link{https://j15h.nu/source/attendance}{Source}}{}
        \item{\small Daily attendance SMS alert for MES College of Engineering students. During the period when project was active, it had more than 2300 registered users (85\% students in the college).}

      \resumeProjectHeading
        {\textbf{Unicalbot} $|$ \link{https://j15h.nu/source/unical}{Source}}{}
        \item{\small A bot that checks university website for updates and exam results and shares them on social media.}


      %\resumeProjectHeading
        %{\textbf{Blender Add-Ons} $|$ \link{https://j15h.nu/source/wall}{Source}, \link{https://j15h.nu/source/library}{Source}}{}
        %\item{\small Developed a set of blender add-ons for architects.}

      %\resumeProjectHeading
        %{\textbf{Publish Your Bookmarks} $|$ \link{https://j15h.nu/source/bookmark}{Source}}{}
        %\item{\small Simple tool to publish Firefox bookmarks as a webpage.}

    \resumeSubHeadingListEnd

\section{Free \& Open Source Software Contributions}
  \vspace{2pt}
  \resumeSubHeadingListStart
\item{
      \projectlink{http://libindic.org}{LibIndic (Silpa)},
      \projectlink{https://github.com/wikimedia/jquery.i18n}{jquery.i18n},
      \projectlink{https://github.com/wikimedia/jquery.ime}{jquery.ime},
      \projectlink{https://github.com/gameclosure/devkit}{Game Closure}, 
      \projectlink{http://www.lineageos.org/}{CyanogenMod / LineageOS}, 
      \projectlink{http://l10n.gnome.org}{GNOME Localization}, 
      \projectlink{https://github.com/smc/fonts}{SMC Fonts},
      \projectlink{https://j15h.nu}{More at https://j15h.nu}
  }
  \resumeSubHeadingListEnd

%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeEducationHeading
      {MES College of Engineering
      }{University of Calicut, Kerala, India}
      {Bachelors degree in Information Technology}{2017 \textbf{--} 2011}
      \resumeSubHeadingListEnd


\updateinfo

\end{document}
